On Secure Delegation of SampBQP with a Classical Client

### 2019-11-25 hamiltonian.tex
Fix typo
Finish another draft of QPIP analysis

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
\end{theorem}

@@

>>>>

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
\end{theorem}

@@

\begin{definition}
	We call the first registers of $\psi_{C(x)}$ the data register, and the later registers of $\psi_{C(x)}$ the time register.
\end{definition}

### 2019-11-25 qpip.tex
Finish another draft of QPIP analysis

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $1-O(T^{-c})$ for any constant $c$.
\end{theorem}
\begin{proof}

	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State $\varepsilon\gets T^{-c}$
			\State Pick $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
			\State Pick $n$ large enough so, $P\left[Bin(n, \frac{1}{2}-\varepsilon)<\left(\frac{1}{2}-2\varepsilon\right)n\right]$ is negligible in $\varepsilon$ by Chernoff bound
			\State Pick $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}=O(\poly(\varepsilon))$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output the other registers
				\EndIf
			\EndFor
			\State Reject
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state at that point as

@@

	$$\norm{\sigma'-\sum_i w_i\rho_i^{\otimes n+m}}=O(\poly(\varepsilon))$$

	TODO set $\tilde{\sigma}$ and fix above to be product measure

	Note that this is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.

	Let $q_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}. By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i q_i}{\sum_j w_j q_j}$.

	Define $J$ to be the set of $j$s where $q_j$ is negligible. TODO negligible shenanigans

	$$\sum_{j\in J} w_j q_j$$

	$$\Rightarrow\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}<\frac{p}{\delta}$$

	Now let $\rho_i$ be with over probability $1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck}. So it is $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.

	So we simply measure the time register until we get a result where we can extract $C(x)$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.

	All errors up to this point is $O(\poly(\varepsilon))$.

>>>>

TODO the following needs $\delta$ parameter
\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$ with completeness negligible to perfect and soundness $1-O(T^{-c})$ for any constant $c$.
\end{theorem}
\begin{proof}

	Set the following variables
	\begin{itemize}
		\item $\varepsilon=T^{-c}$
		\item $m$ large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
		\item $n$ large enough so by Chernoff bound:
			\begin{itemize}
				\item[$\circ$] $q'=P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
				\item[$\circ$] $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ is negligible in $\varepsilon$
			\end{itemize}
		\item $N$ large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\end{itemize}

	We claim that the following protocol does what is required:
	\floatname{algorithm}{Protocol}
	\begin{algorithm}
		\caption{Our $\QPIP_{XZ}$ protocol}
		\label{AlgAmp1}
		\begin{algorithmic}[1]
			\State The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
			\State The verifier randomly picks $n+m$ copies in sequence and without replacement
			\State The verifier runs \autoref{AlgGroundStateCheck} on $n$ of the copies
			\If{over $(\frac{1}{2}-\varepsilon)n$ copies accept}
			\For{$i\gets 1, m$}
				\State Measure the time register of a fresh copy from the prover
				\If{Measured $t\geq T$}
					\State Measure and output its data register
				\EndIf
			\EndFor
			\State Reject
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	This clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover. Let $\sigma$ be the state the prover sends.

	Picking $n+m$ out of $N$ registers is equivalent to first applying a random permutation then taking the first $n+m$ registers. Denote the state after the random permutation as

@@

	$$\max_{\Lambda_i}\norm{\Lambda_1\otimes\ldots\otimes\Lambda_{m+n}(\sigma'-\sum_i w_i\rho_i^{\otimes n+m})}=O(\varepsilon)$$

	Note that $\tilde\sigma=\sum_i w_i\rho_i^{\otimes n+m}$ is a classical probability distribution over inputs $\rho_i^{\otimes n+m}$ with $w_i$ as weights.

	Let $p_i$ be the accept probability of at least $(\frac{1}{2}-\varepsilon)n$ copies from $\rho_i^{\otimes n}$ accept under \autoref{AlgGroundStateCheck}.
	So the accept chance of this prover is $\sum_j w_j p_j>\delta$
	By Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\ket{\rho_i^{\otimes n+m}}$ is then $\frac{w_i p_i}{\sum_j w_j p_j}$.

	Let
	$$J=\set{j:q_j\leq q'}$$

	Then the following is clearly negligible:
	$$\sum_{j\in J} w_j q_j$$

	And so is
	$$\frac{\sum_{j\in J} w_j q_j}{\sum_i w_i q_i}$$

	So by Bayes' theorem, conditioned on acceptance, the probability of $\tilde{\sigma}$ being $\rho_i^{\otime n+m}$ where $\rho_i$ has over probability $\1-2\varepsilon$ to be accepted by \autoref{AlgGroundStateCheck} is overwhelming.

	Such $\rho_i$ are $O(\poly(\varepsilon))$-close to $\ket{\psi_{C(x)}}$.

	So we simply measure the time register until we get measurement result $t\geq T$. The probability of failing to do so after all $m$ copies is $\frac{1}{2^m}$ which is negligible.

	Once we do measure $t\geq T$, the data register is guaranteed to be $O(\poly(\varepsilon))$-close to $C(x)$.

	All errors up to this point is $O(\varepsilon)$.
